A pipeline to analyse time-course gene expression data

### 2019-07-31 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\begin{verbatim}
##   
   checking for file '/tmp/RtmpLM5IuQ/remotes347f085d5d/NelleV-moanin-205e154/DESCRIPTION' ...

v  checking for file '/tmp/RtmpLM5IuQ/remotes347f085d5d/NelleV-moanin-205e154/DESCRIPTION'
##

@@

-  building 'moanin_0.0.0.tar.gz' (3.5s)
##

>>>>

\begin{verbatim}
##   
   checking for file '/tmp/RtmpWctcMt/remotes3475772588/NelleV-moanin-205e154/DESCRIPTION' ...

v  checking for file '/tmp/RtmpWctcMt/remotes3475772588/NelleV-moanin-205e154/DESCRIPTION'
##

@@

-  building 'moanin_0.0.0.tar.gz' (3.6s)
##
